HEP Software Foundation Community White Paper Working Group -- Training, Staffing and Careers

### 2018-07-03 CWP/papers/HSF-CWP-2017-02_training/latex/cwp-wg-training-careers.tex
Add some references and correct a few last points in the training paper

Another challenge is the wide heterogeneity in
student competence. Special care must be given to setup
a training structure that can cope with both beginners and advanced students.
This may rest on a low granularity subdivision of independant topics.
The IN2P3 authors try to restrict their tutorials to 20 minutes
of material, as inspired by the Pomodoro technique, so that one can easily jump
and compose one's own ``menu''. However, it turns out to be tricky to keep such
small tutorials really independant and meaningful when they can be selected at
will.

All trainers have also faced the tremendous loss of time
in software installation for any practical exercises as many students have
not managed to prepare their machines in advance.
Here containers may bring real
progress, provided that everyone has at least Docker installed on their machine.
JupyterHub, also, is a technology which enable training session with
no need for installation (but with a need for network).

@@

The HEP community by and large acknowledges and recognizes the great importance
of training in the field of scientific computing. This activity should encompass
several types of {\it students}, from undergraduates, to young researchers, up
to senior physicists, all of them in need of an appropriately designed training
path in order to be proficent in their scientific endevours.

@@

For each of these points we provide an overview of the current situation and possible proposals to build a roadmap.

>>>>

Another challenge is the wide heterogeneity in
student competence. Special care must be given to setup
a training structure that can cope with both beginners and advanced students.
This may rest on a low granularity subdivision of independant topics.
The IN2P3 authors try to restrict their tutorials to 20 minutes
of material, as inspired by the Pomodoro technique\cite{PomodoroTechnique}, so
that one can easily jump and compose one's own ``menu''. However, it turns out to be tricky to keep such
small tutorials really independant and meaningful when they can be selected at
will.

All trainers have also faced the tremendous loss of time
in software installation for any practical exercises as many students have
not managed to prepare their machines in advance.
Here containers may bring real
progress, provided that everyone has at least Docker\cite{Docker} installed on
their machine.
JupyterHub\cite{JupyterHub}, also, is a technology which enable training session
with no need for installation (but with a need for network).

@@

The HEP community by and large acknowledges and recognizes the great importance
of training in the field of scientific computing. This activity should encompass
several types of {\it students}, from undergraduates, to young researchers, up
to senior physicists, all of them in need of an appropriately designed training
path in order to be proficent in their scientific endeavours.

@@

For each of these points we have provided an overview of the current situation
and made proposals to improve the situation in HEP.
